A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-08-10 meth.tex
updating workflow figure
adding much cleaner 5-region figure

\begin{figure}
  \begin{center}
    \includegraphics[height=0.85\textheight]{aneris-workflow.pdf}
    \caption[]{
      \label{fig:workflow}
      The full harmonization process as executed by \code{aneris}. Operations
      that can be configured with user-based input configurations are shown in
      purple. The core harmonization process is shown in yellow.  }
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.85\textwidth]{regions.png}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the RCPs with their 11-region constituents: Asia
      (Central Asia, South Asia, Pacific Asia), Latin America, the Middle East
      and Africa, the OECD (North America, Western Europe, and Pacific OECD),
      Reforming Economies (Eastern Europe and Former Soviet Union).
    }
  \end{center}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[height=0.9\textheight]{aneris-workflow.pdf}
    \caption[]{
      \label{fig:workflow}
      The full harmonization process as executed by \code{aneris}. Operations
      that can be configured with user-based input configurations are shown in
      purple. The core harmonization process is shown in yellow.  }
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{MESSAGE_11-5regions_map.pdf}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the RCPs with their 11-region constituents: Asia
      (Central Asia, South Asia, Pacific Asia) [yellows], Latin
      America [magenta], the Middle East and Africa [greens], the OECD (North
      America, Western Europe, and Pacific OECD) [blues], Reforming Economies
      (Eastern Europe and Former Soviet Union) [reds].  }
  \end{center}
\end{figure}
